Multitasking Interfaces on Touchscreen Mobile Devices

### 2015-12-08 sigchi-latex-proceedings 2/final-paper.tex
Add Keywords and Title

\title{HCI Final Paper}

\numberofauthors{5}
\author{
    Kyra Assaad, Zach Munro-Cape, Ajit Pawar, Ishan Thukral, \& Colin White\\
  \sharedaffiliation
      \affaddr{Department Computer Science }  \\
      \affaddr{University of Toronto }   \\
      \affaddr{Toronto, Ontario} \\
      \email{\{kyra.assaad,zach.munro.cape,ajit.pawar,ishan.thukral,colin.white\}@mail.utoronto.ca }
}

%\author{%
%  \alignauthor{Ajit Pawar\\
%    \affaddr{University of Toronto}\\
%    \affaddr{Toronto, Ontario}\\
%    \email{ajit.pawar@mail.utoronto.ca}}\\
% \alignauthor{Colin White\\
%    \affaddr{University of Toronto}\\
%    \affaddr{Toronto, Ontario}\\
%    \email{colin.white@mail.utoronto.ca}}\\
%  \alignauthor{Ishan Thukral\\
%    \affaddr{University of Toronto}\\
%    \affaddr{Toronto, Ontario}\\
%    \email{ishan.thukral@mail.utoronto.ca}}\\
% \alignauthor{Kyra Assaad\\
%    \affaddr{University of Toronto}\\
%    \affaddr{Toronto, Canada}\\
%    \email{kyra.assaad@mail.utoronto.ca}}\\
%  \alignauthor{Zach Munro-Cape\\
%    \affaddr{University of Toronto}\\
%    \affaddr{Toronto, Ontario}\\
%    \email{zach.munro.cape@mail.utoronto.ca}}\\
%}

@@

@@

>>>>

\title{Multitasking Interfaces on Touchscreen Mobile Devices}

\numberofauthors{5}

%\author{
%    Kyra Assaad, Zach Munro-Cape, Ajit Pawar, Ishan Thukral, \& Colin White\\
%  \sharedaffiliation
%      \affaddr{Department Computer Science }  \\
%      \affaddr{University of Toronto }   \\
%      \affaddr{Toronto, Ontario} \\
%      \email{\{kyra.assaad,zach.munro.cape,ajit.pawar,ishan.thukral,colin.white\}@mail.utoronto.ca }
%}

\author{%
  \alignauthor{Ajit Pawar*\\
    \affaddr{University of Toronto}\\
    \affaddr{Toronto, Ontario}\\
    \email{ajit.pawar@mail.utoronto.ca}}\\
 \alignauthor{Colin White\\
    \affaddr{University of Toronto}\\
    \affaddr{Toronto, Ontario}\\
    \email{colin.white@mail.utoronto.ca}}\\
  \alignauthor{Ishan Thukral\\
    \affaddr{University of Toronto}\\
    \affaddr{Toronto, Ontario}\\
    \email{ishan.thukral@mail.utoronto.ca}}\\
 \alignauthor{Kyra Assaad\\
    \affaddr{University of Toronto}\\
    \affaddr{Toronto, Canada}\\
    \email{kyra.assaad@mail.utoronto.ca}}\\
  \alignauthor{Zach Munro-Cape\\
    \affaddr{University of Toronto}\\
    \affaddr{Toronto, Ontario}\\
    \email{zach.munro.cape@mail.utoronto.ca}}\\
}

@@

*Authors arranged alphabetically by first name.

@@

\section{keywords}
Multitasking; Task switching interfaces; Mobile
